---
title: "Milestone 2 Report"
author:
    - YOUR_NAME
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    keep_md: yes
urlcolor: blue
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Instructions:** Complete the relevant parts of this template.
Delete the instructions sections before submission so they are not included in your word count. 

## Research Question

**Instructions:** Re-state your research question from Milestone 1. 
If you have further refined it, that is OK.

## Literature Review

### Three Most Relevant Papers

**Instructions:** Complete the review templates for the three papers you deem most relavant to your project.
The repository's README file provides some further details on what to include for each component.

#### Paper 1

* **Citation:**
* **Research Question**:
* **Question Type:**
* **Main Data Source**:
* **Methods:**
* **Main takeaway**:

#### Paper 2

* **Citation:**
* **Research Question**:
* **Question Type:**
* **Main Data Source**:
* **Methods:**
* **Main takeaway**:

#### Paper 3

* **Citation:**
* **Research Question**:
* **Question Type:**
* **Main Data Source**:
* **Methods:**
* **Main takeaway**:

### Relevant Blog Posts (if any)

**Instructions:** Provide the name and link to any blog posts you have found that are relevant to your final project.
These can be either related to the marketing topic, or the statistical methods you plan to use.
If there are none, write "None."

* ...

## Exploratory Data Analysis

**Instructions:** Provide **EITHER** a descriptive table **OR** a descriptive figure that motivates further analysis.
Typically this will show some evidence suggesting a pattern in the data you will be aiming to document that you will explore further in Milestone 3.
Describe your findings in a short paragraph (i.e. max 5 sentences).

**Delete headings, code chunks and text below as appropriate.**

### (OPTION 1) Descriptive Table

```{r, echo = FALSE}
# LOAD NEEDED LIBRARIES HERE
```

```{r, echo = FALSE}
# WRITE CODE TO:
# (i) LOAD DATA
# (ii) CLEAN DATA AS NEEDED
```

```{r}
# WRITE CODE TO PRODUCE TABLE
```

(INSERT PARAGRAPH DESCRIBING TAKEAWAYS)

### (OPTION 2) Descriptive Figure

```{r, echo = FALSE}
# LOAD NEEDED LIBRARIES HERE
```

```{r, echo = FALSE}
# WRITE CODE TO:
# (i) LOAD DATA
# (ii) CLEAN DATA AS NEEDED
```

```{r}
# WRITE CODE TO PRODUCE FIGURE
```

(INSERT PARAGRAPH DESCRIBING TAKEAWAYS)

## Word Count

Number of Words: `r wordcountaddin::word_count("milestone-02.Rmd")`

## References